Tree height and hydraulic traits shape growth responses across droughts in a temperate broadleaf forest

### 2019-11-05 manuscript/climate_sensitivity_draft.Rmd
1.5 line spacing

---
title: "Tree height and hydraulic traits shape growth responses across droughts in a temperate broadleaf forest"
author: "Ian McGregor, Ryan Helcoski, Norbert Kunert, Alan Tepley, Erika Gonzalez-Akre, Valentine Herrmann, Joseph Zailaa, Atticus Stovall, Norman Bourg?, William McShea?, Neil Pederson, Lawren Sack, Kristina Anderson-Teixeira"
output:
  pdf_document:
    citation_package: natbib
    fig_caption: yes
bibliography: ["book.bib",  "packages.bib"]
biblio-style: "apalike"
csl: apa.csl
header-includes:
- \usepackage{float}
- \usepackage{booktabs}
- \usepackage{pdflscape}
- \newcommand{\blandscape}{\begin{landscape}}
- \newcommand{\elandscape}{\end{landscape}}
- \usepackage{caption}
- \captionsetup[table]{font=small}
- \captionsetup[figure]{font=small}
- \captionsetup[table]{labelformat=empty}
- \captionsetup[figure]{labelformat=empty}
- \usepackage{dcolumn} #for sidewaystable
---

>>>>

---
title: "Tree height and hydraulic traits shape growth responses across droughts in a temperate broadleaf forest"
author: "Ian McGregor, Ryan Helcoski, Norbert Kunert, Alan Tepley, Erika Gonzalez-Akre, Valentine Herrmann, Joseph Zailaa, Atticus Stovall, Norman Bourg?, William McShea?, Neil Pederson, Lawren Sack, Kristina Anderson-Teixeira"
output:
  pdf_document:
    citation_package: natbib
    fig_caption: yes
bibliography: ["book.bib",  "packages.bib"]
biblio-style: "apalike"
csl: apa.csl
header-includes:
- \usepackage{setspace}\onehalfspacing
- \usepackage{float}
- \usepackage{booktabs}
- \usepackage{pdflscape}
- \newcommand{\blandscape}{\begin{landscape}}
- \newcommand{\elandscape}{\end{landscape}}
- \usepackage{caption}
- \captionsetup[table]{font=small}
- \captionsetup[figure]{font=small}
- \captionsetup[table]{labelformat=empty}
- \captionsetup[figure]{labelformat=empty}
- \usepackage{dcolumn} #for sidewaystable
---
